Commutative Character Sheaves

### 2015-11-03 followup.tex
Corrections to the essential image of the forgetful functor CS_H(G) --> CS(G).

Suppose there is some $H\times G\to G\times G$ such that the following diagram commutes.
\[
\begin{tikzcd}
&  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
G & & G \\
& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p} & 
\end{tikzcd}
\]
Then $f_1 : H\times G \to G$ and $f_0 : H \to G$ . . .

\begin{lemma}
If $f: H\times G \to G$ exists as above and $f_1$ is proper, then the forgetful functor $\CS_H(G) \to \CS(G)$ is full and faithful, with essential image
$\CS'(G)$ consisting of those $(\cs{L},\mu,\nu) \in \CS_H(G)$ such that $f_0^*\cs{L} \iso (\EE)_{H}$. 
\end{lemma}

@@

We now consider a special case of the lemmas above. 
Suppose $H = G$ and the action $a$ is $m: G\times G\to G$.
Suppose $H' = G\der$ and let $a'$, be the restriction of $m$ to $G\der\times G$.
Let $d : G\der \hookrightarrow G$ and set $k(h,g) = d(h)$. 
Then $f : G\der \times G\to G\times G$ is simply the inclusion.

>>>>

Suppose there is some $f : H\times G\to G\times G$ such that the following diagram commutes.
\[
\begin{tikzcd}
&  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
G & & G \\
& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p} & 
\end{tikzcd}
\]
Then $f(h,g) = (f_1(h,g),p)$ for $f_1 : H\times G \to G$.
Let $\CS'(G)$ be the full subcategory of $\CS(G)$ consisting of those $(\cs{L},\mu,\nu) \in \CS_H(G)$ such that $f_1^*\cs{L} \iso (\EE)_{H\times G}$.

\begin{lemma}
The forgetful functor $\CS_H(G) \to \CS(G)$ is full and faithful with essential image $\CS'(G)$.\end{lemma}

@@

We now consider a special case of the lemmas above. 
Suppose $H = G\der$ and the action $a$ is the restriction of $m$ to $G\der\times G$.
Then $f : G\der \times G\to G\times G$ is simply the inclusion and $f_1: G\der\times G \to G$ is projection to the first coordinate followed by inclusion $G\der \hookrightarrow G$.
